---
output:
  pdf_document: default
  html_document: default
---

The data provided needs some cleaning up like removing NaN's, deleting the columns added by mistake and finally having the data ready for applying algorithms.

```{r dataPreProcess}

vehicleData <- subset(vehicleData, select=-county)
prev_length = nrow(vehicleData)
vehicleData <- vehicleData[rowSums(is.na(vehicleData)) == 0,]
new_length = nrow(vehicleData)
```

As we saw in table \ref{tab:dataDesc}, there was a column named "county" which we need to remove since it was mistakenly added. Also, initially there are `r toString(prev_length)` rows and after dropping NaNs we now have `r toString(new_length)` i.e. we removed `r toString(prev_length-new_length)` entries.

```{r omitColumns}

remove_cols = c("url", "region_url", "description", "image_url")

vehicleData <- subset(vehicleData, 
                       select = -c(url, region_url, description, image_url))
```

Since not all columns would be useful for Machine Learning purposes, We will only be using a subset of this data for our analysis and the columns that we will be removing are: `r toString(remove_cols)` leaving us with the following columns: `r toString(colnames(vehicleData))`.