---
title: 'Data Driven Knowledge Discovery Final Exam - Summer 2022'
author: "Rahul Golhar"
date: "8/9/2022"
output:
  pdf_document:
    latex_engine: xelatex
    toc: true
    toc_depth: 3
    fig_caption: yes
  word_document: default
  html_document:
    df_print: paged
fig_caption: yes
tab_caption: yes
header-includes:
 \usepackage{float}
 \floatplacement{figure}{H}
subtitle: Analysis of Craigslist Vehicle Postings Data
---

\pagenumbering{gobble} 
\newpage              
\pagenumbering{arabic}


# Introduction
This is the document for the final examination submitted by Rahul Golhar for the course ISTE 780 - Data Driven Knowledge Discovery taught by Prof. Mick McQuaid in the Summer 2022 term at Rochester Institute of Technology.


```{r setup, include=FALSE}

library(tidyverse)
library(dtplyr)
library(arrow)
library(stringr)
library( kableExtra )
knitr::opts_chunk$set(tidy.opts = list(width.cutoff = 30), 
                      tidy = TRUE, echo = FALSE,warning = FALSE, message = FALSE,dev = "cairo_pdf" )
```

We start by reading the data into 2 data frames, one for metadata from file 'vehicles.dat' and one for the actual data from 'vehicles.csv'. Each column is also given a data type while reading.

```{r readData, echo=TRUE}
# metadata file path
metadataFilename = "./data/vehicles.dat"

# vehicles data file path
vehicledataFilename = "./data/vehicles.csv"

# read metadata table from file
metadata <- data.table::fread(metadataFilename, colClasses = c("integer", "character", "character"))

# read vehicles data table from file
vehicleData <- data.table::fread(vehicledataFilename, header = TRUE, 
    colClasses = c(
        "numeric", "character", "character","character",
        "numeric", "numeric", "character", "character",
        "character", "character", "character", "numeric",
        "character", "character", "character","character",
        "character", "character", "character","character",
        "character", "character", "character","numeric",
        "numeric", "character"), na.strings = c("", "NA"))
```

# Data Description
```{r dataDesc, child="dataDescription.Rmd"}
```

# Data Pre-processing
```{r dataPreProcess, child="dataPreProcessing.Rmd"}
```

# Data Visualization
```{r mapViz, child="mapViz.Rmd"}
```

# Linear Regression
```{r linearRegression, child="linearRegression.Rmd"}
```
