---
title: 'Data Driven Knowledge Discovery Final Exam - Summer 2022'
author: "Rahul Golhar"
date: "8/6/2022"
output:
  pdf_document:
    latex_engine: xelatex
    toc: true
    toc_depth: 3
    fig_caption: yes
  word_document: default
  html_document:
    df_print: paged
fig_caption: yes
tab_caption: yes
header-includes:
 \usepackage{float}
 \floatplacement{figure}{H}
subtitle: Analysis of Craigslist Vehicle Postings Data
---

\pagenumbering{gobble} 
\newpage              
\pagenumbering{arabic}


# Introduction
This is the document for final examination submitted by Rahul Golhar for the course ISTE 780 - Data Driven Knowledge Discovery taught by Prof. Mick McQuaid in the Summer 2022 term at Rochester Institute of Technology.


```{r setup, include=FALSE}

#library( doParallel )
library(tidyverse)
library(dtplyr)
library(arrow)
library(stringr)
library( kableExtra )
#library(glmnet)
#library(caret)
#library(randomForest)
knitr::opts_chunk$set(tidy.opts = list(width.cutoff = 30), 
                      tidy = TRUE, echo = FALSE,warning = FALSE, message = FALSE,dev = "cairo_pdf" )
#registerDoParallel(cl=8,cores=4)
```

```{r readData}
metadataFilename = "./data/vehicles.dat"
vehicledataFilename = "./data/vehicles.csv"

metadata <- data.table::fread(metadataFilename, colClasses = c("integer", "character", "character"))
vehicleData <- data.table::fread(vehicledataFilename, header = TRUE, 
    colClasses = c(
        "integer", "character", "character","character",
        "integer", "integer", "character", "character",
        "character", "integer", "character", "double",
        "character", "character", "character","character",
        "character", "character", "character","character",
        "character", "character", "character","double",
        "double", "character"), na.strings = c("", "NA"))
```
# Data Description
```{r dataDesc, child="dataDescription.Rmd"}
```

# Data Pre-processing
```{r dataPreProcess, child="dataPreProcessing.Rmd"}
```

# Supervised Learning

## Linear Regression
```{r linearRegression, child="./algorithms/linearRegression.Rmd"}
```

## Logistic Regression
```{r logisticRegression, child="./algorithms/logisticRegression.Rmd"}
```

# Unsupervised Learning

## K Means Clustering
```{r kMeansClustering, child="./algorithms/kMeansClustering.Rmd"}
```

## Hierarchical clustering
```{r hierarchicalClustering, child="./algorithms/hierarchicalClustering.Rmd"}
```