---
output:
  pdf_document: default
  html_document: default
--- 


For this algorithm, we predict "Price" of the car based on various factors using linear regression models. For this task we use columns: "price"(label), "year", "manufacturer", "odometer", "condition", "fuel", "transmission", "drive", "size", "type" and "paint_color". Before we start, we need to get the data ready and factorize the categorical columns i.e. the columns except "year" and "odometer".

```{r linreg, echo=TRUE}

library(caret)

# get the subset of data
linRegData <- subset(vehicleData, 
                       select = c(price, year, manufacturer, odometer,
                                  condition, fuel, transmission, drive,
                                  size, type, paint_color))

# Factor the data from
linRegData$manufacturer <-linRegData$manufacturer<-as.factor(linRegData$manufacturer)
linRegData$condition <-linRegData$condition<-as.factor(linRegData$condition)
linRegData$fuel <-linRegData$fuel<-as.factor(linRegData$fuel)
linRegData$transmission <-linRegData$transmission<-as.factor(linRegData$transmission)
linRegData$drive <-linRegData$drive<-as.factor(linRegData$drive)
linRegData$size <-linRegData$size<-as.factor(linRegData$size)
linRegData$type <-linRegData$type<-as.factor(linRegData$type)
linRegData$paint_color <-linRegData$paint_color<-as.factor(linRegData$paint_color)
```

Now our data is ready for further steps.

```{r trainTestSplit, echo=TRUE}
set.seed(1)

# get rows to split data for training and testing purposes
train_entries <- sort(sample(nrow(linRegData), nrow(linRegData) * 0.8))

# read data for training and testing sets
train_data = linRegData[train_entries,]
test_data = linRegData[-train_entries,]
```

Once we are done with getting the data ready, we split it into training and testing sets with a split of 80% and 20% respectively. So, now we have a training set of `r toString(dim(train_data)[1])` entries and a testing set of `r toString(dim(test_data)[1])`.


## Predict Price using entry year and miles travelled by the vehicle

Here, we develop a model to predict "Price" using fields "year" and "odometer" and train it.

```{r linreg_model_1, echo=TRUE}
linreg_model_1 <- lm(formula = price ~ 
                  year+odometer,
  # year+manufacturer+odometer+condition+fuel+transmission+drive+size+type+paint_color,
                data = train_data)
```

The summary of this model can be found below:
```{r summary_linreg_model_1, echo=TRUE}
summary(linreg_model_1)
```

Let's have a look at the performance of this model:

We calculate Residual Sum of Squares for training data which measures the amount of error remaining between the regression function and the data set after the model has been run.

```{r metrics_linreg_model_1, echo=TRUE}
# calculate Residual Sum of Squares Error
linreg_model_1_RSS<- c(crossprod(linreg_model_1$residuals))

# Calculate Mean Squared error by averaging RSS
linreg_model_1_MSE <- linreg_model_1_RSS / length(linreg_model_1$residuals)

# Calculate Root Mean Squared Error 
linreg_model_1_RMSE <- sqrt(linreg_model_1_MSE)
```
Residual Sum of Squares Error: `r toString(linreg_model_1_RSS)`

Mean Squared Error: `r toString(linreg_model_1_MSE)`

Root Mean Squared Error: `r toString(linreg_model_1_RMSE)`

Now, we need to see how the model performs on the testing data. We calculate the predictions and then the $R^2$ score of these predictions.

```{r testing_linreg_model_1, echo=TRUE}
# predict the results of the model on testing data
linreg_model_1_predictions <- linreg_model_1 %>% predict(test_data)

# calculate the R2 score of the predictions
linreg_model_1_R2 <- R2(linreg_model_1_predictions, test_data$price)
```
$R^2$ score of the predictions: `r toString(linreg_model_1_R2)`



## Predict Price using multiple columns

Here, we develop a model to predict "Price" using the fields: "year", "manufacturer", "odometer", "condition", "fuel", "transmission", "drive", "size", "type" and "paint_color" and train it.

```{r linreg_model_2, echo=TRUE}
linreg_model_2 <- lm(formula = price ~
                       year+manufacturer+odometer+condition+
                       fuel+transmission+drive+size+type+paint_color,
            data = train_data)
```

**The summary of this model can be found by uncommenting the code below. It is commented because it takes a few pages of space.**
```{r summary_linreg_model_2, echo=TRUE}
#summary(linreg_model_2)
```

Let's have a look at the performance of this model:

Similar to previous model, we calculate Residual Sum of Squares, Mean Squared Error and Root Mean Squared Error.

```{r metrics_linreg_model_2, echo=TRUE}
# calculate Residual Sum of Squares Error
linreg_model_2_RSS<- c(crossprod(linreg_model_2$residuals))

# Calculate Mean Squared Error by averaging RSS
linreg_model_2_MSE <- linreg_model_2_RSS / length(linreg_model_2$residuals)

# Calculate Root Mean Squared Error 
linreg_model_2_RMSE <- sqrt(linreg_model_2_MSE)
```
Residual Sum of Squares Error: `r toString(linreg_model_2_RSS)`

Mean Squared Error: `r toString(linreg_model_2_MSE)`

Root Mean Squared Error: `r toString(linreg_model_2_RMSE)`

Now, we need to see how the model performs on the testing data. We calculate the predictions and then the $R^2$ score of these predictions.

```{r testing_linreg_model_2, echo=TRUE}
# predict the results of the model on testing data
linreg_model_2_predictions <- linreg_model_2 %>% predict(test_data)

# calculate the R2 score of the predictions
linreg_model_2_R2 <- R2(linreg_model_2_predictions, test_data$price)
```
$R^2$ score of the predictions: `r toString(linreg_model_2_R2)`





## Tuning

```{r test}
library(leaps)
library(Metrics)

linreg_model_best <- regsubsets(price ~
                       year+odometer+condition+fuel+transmission+drive+size+type+paint_color,
                       data = train_data, nvmax = 10,really.big=T)

```

```{r linreg_model_best_adjr2, fig.cap="\\label{fig:linreg_model_best_adjr2}Adjusted R^2 Contribution for Price+Odometer Speeds"} 

#look at adj r^2
plot(summary(linreg_model_best)$adjr2,xlab="Predictor Rank", ylab = "Adjusted R^2", main = "Price+Odometer", pch = 16)
```

## Conclusion

Since "Price" is a quantitative value, I decided to predict it using the most commonly looked at factors which are odometer reading and the year of the model since these 2 factors talk about the age of the car and it's usage and age. It can be observed that the errors were very high for this model.
